An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-23 VLDB2026/main.tex
Update main.tex

	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) and 256GB of RAM.  \textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM.} Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}. By default, queries run on a single thread. We also report results for 16-thread parallelism in specific scenarios.

	We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}. For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on the same server configuration, with results presented in Figure~\ref{fig:Different_Computer_range}. When compared with the original server's experimental results shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}

>>>>

	We conduct all experiments on a server running Ubuntu 20.04, equipped with an AMD EPYC 7K62 processor (2.6GHz) and 256GB of RAM.  \textcolor{cyan}{Additionally, to investigate the impact of different server configurations on algorithm performance, we also conducted partial experiments on a server equipped with dual Intel(R) Xeon(R) Gold 6330 CPU @ 2.00GHz and 128GB of RAM. For clarity and conciseness, we hereafter refer to the former as Server A and the latter as Server B. Unless otherwise specified, all experiments were conducted on Server A.}

	Unless otherwise stated, we execute index construction with 32 threads to accelerate the process~\cite{benchmarkindex}. By default, queries run on a single thread. We also report results for 16-thread parallelism in specific scenarios. We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}. For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}} 
	\textcolor{cyan}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on Server B using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on Server A shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}f, the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency and smaller RAM capacity of Server B compared to Server A, the QPS values are slightly lower across all methods.}
%	\textcolor{red}{To investigate the impact of different server configurations on the performance of the algorithms, we conducted additional experiments on a server equipped with two Intel(R) Xeon(R) Gold 6330 CPUs @ 2.00GHz using the YT-Audio-Real dataset, and the results are shown in Figure~\ref{fig:Different Computer}. Compared with the experimental results on the original server (as shown in Figure~\ref{fig:exp_1_1_SingleLabel_1thread}(f)), the relative ranking of the algorithms remains largely unchanged, indicating that the performance of these methods is not significantly affected by differences in CPU configurations. Due to the lower CPU frequency of the Xeon 6330 compared to the original server, the QPS values are slightly lower across all methods.}

@@

	\textit{\textbf{\textcolor{blue}{Different Hardware Environments.}}}
	\textcolor{cyan}{As described in Section 4.2.4, we performed additional range filtering experiments using the YT-Audio-Real dataset on Server B, with results presented in Figure~\ref{fig:Different_Computer_range}. When compared with the experimental results of Server A shown in Figure~\ref{fig:exp_8_2}a, our findings remain consistent with those reported in Section 4.2.4. For brevity and due to space limitations, we omit further discussion of these redundant results.}
%	\textcolor{cyan}{Consistent with Section 4.2.4, we conducted additional range filtering experiments using the YT-Audio-Real dataset on the same server, with results shown in Figure \ref{fig:Different Computer range}. Compared with the original server's experimental results (Figure \ref{fig:exp_8_2}($e$)), the conclusions remain identical to those described in Section 4.2.4. Due to space constraints, these details are not reiterated here.}
